Scientific Team Project

### 2018-04-23 Presentations/Milestone1/presentation.tex
Add schedule to presentation
Update presentation.tex
Add big picture
Reworked parts of presentation1

\section{Introduction}
	\begin{frame}
		\frametitle{Introduction}
		\begin{itemize}
			\item \emph{In computer programming, a thread pool is a software design pattern for achieving concurrency of execution in a computer program.}
			\item Pool of Threads
			\item Reduces overhead of creating new threads by reusing existing threads.
		\end{itemize}
	\end{frame}
	\begin{frame}
		\frametitle{Current Situation}
		\begin{itemize}
			\item Operations are spawning dozens of threads, which are not handled and managed..
			\item After some operations profilers dies.
		\end{itemize}
	\end{frame}

	\begin{frame}
		\frametitle{Desirable Situation}
		\begin{itemize}
			\item Reuse of Threads with thread pools.
			\item Limited amount of threads, which are handled correctly.
		\end{itemize}
	\end{frame}

>>>>

\section{Motivation}
	\begin{frame}
		\frametitle{Motivation}
		\begin{center}
			\includegraphics[width=0.6\textwidth]{img/bigpicture.png}
		\end{center}
	\end{frame}

\section{Introduction}
	\begin{frame}
		\frametitle{Introduction}
		\begin{itemize}
			\item \emph{In computer programming, a thread pool is a software design pattern for achieving concurrency of execution in a computer program.}
			\item Pool of Threads to distribute parallel tasks
			\item Reduces overhead of creating new threads by reusing existing threads.
		\end{itemize}
	\end{frame}

	\begin{frame}
		\frametitle{Current Situation}
		\begin{itemize}
			\item Operations are spawning dozens of threads, which are not handled and managed..
			\item Heavy overhead of creating and removing threads
			\item After some operations profiler dies (too many threads).
			\item Debugging/Profiling not possible due to number of threads 
		\end{itemize}
	\end{frame}

	\begin{frame}
		\frametitle{Desirable Situation}
		\begin{itemize}
			\item Reuse of Threads with thread pools.
			\item Reduce overhead of thread management
			\item Improve maintainability of parallel code
			\item Defy competition to existing thread pool libs
		\end{itemize}
	\end{frame}

\section{Planning}

\begin{frame}
	\frametitle{Team Roles}
	\begin{figure}
		\includegraphics[width=0.7\linewidth]{img/TeamRoles}
	\end{figure}
\end{frame}

\begin{frame}
	\frametitle{Schedule}
	\includegraphics[width=1.0\textwidth]{img/schedule.png}
\end{frame}
